A Standardized Effect Size for Evaluating the Strength of Phylogenetic Signal, and Why Lambda is not Appropriate

### 2020-04-28 Manuscript/Manuscript-3.tex
vsn 3

\textbf{Keywords}: phylogenetic signal, effect size, Pagel's lambda
\hfill\break

\textbf{Short Title}: An Effect Size for Phylogenetic Signal
\hfill\break

@@

\{conclusion holds: interpreting the regression is not appreciably
different (in terms of slopes and f values)\}

@@

Evolutionary biologists commonly seek to describe the relative strength
of phylogenetic signal in phenotypic traits, to determine the extent to
which shared evolutionary history has influenced trait covariation among
taxa. This is often accomplished by interpreting empirical estimates of
\(\lambda\); with smaller values signifying `weak' phylogenetic signal,
while larger values are interpreted as `strong' phylogenetic signal
(e.g., De Meester et al. 2019; Pintanel et al. 2019; Su et al. 2019).
Other approaches for interpreting \(\lambda\) are more statistical. For
instance, some have evaluated whether the observed \(\lambda\) differs
from some expected value through the use of confidence intervals
(Vandelook et al. 2019) or by performing likelihood ratio tests that
compare the observed model fit to that obtained when \(\lambda=0\) or
\(\lambda=1\) (Freckleton et al. 2002; Cooper et al. 2010; Bose et al.
2019). Additionally, qualitative comparisons of \(\lambda\) estimates
obtained from multiple phenotypic traits have been used to infer whether
the strength of phylogenetic signal is greater in one trait as compared
to another (e.g., Liu et al. 2019; Bai et al. 2019). Indeed, statements
regarding the strength of phylogenetic signal based on \(\lambda\) are
rather common in the evolutionary literature. We conducted a literature
survey in Google.scholar and found that of the 204 papers published in
2019 that estimated and reported Pagel's \(\lambda\), 40\% interpreted
the strength of phylogenetic signal for at least one phenotypic trait.
Additionally, because nearly half of the 1,572 \(\lambda\) values
reported were near the limits of the parameter (Figure 1), this
percentage is even higher, as biological interpretation of phylogenetic
signal at the limits of \(\lambda\) are known. \hfill\break

@@

In this study, we evaluate the precision of Pagel's \(\lambda\) in
estimating known levels of phylogenetic signal in phenotypic data. We
use computer simulations with differing numbers of species, differently
shaped phylogenies, and differing input levels of phylogenetic signal,
to explore the degree to which \(\lambda\) correctly identifies known
levels of phylogenetic signal, and under what circumstances. We find
that while PGLS parameters (e.g., \(\beta\)) are accurately estimated
with the inclusion of phylogenetic signal, estimates of \(\lambda\) are
not. We also find that estimates of \(\lambda\) vary widely for a given
input value of phylogenetic signal, and that the precision in estimating
\(\lambda\) is not constant across the range of input signal, with
decreased precision when phylogenetic signal is of intermediate
strength. Additionally, the same estimated values of \(\lambda\) may be
obtained from datasets containing vastly different input levels of
phylogenetic signal. Thus, \(\lambda\) is not a reliable estimate of the
strength of phylogenetic signal in phenotypic data. We subsequently
derive a standardized effect size for measuring the strength of
phylogenetic signal in phenotypic datasets, and apply the concept to two
common measures of phylogenetic signal: \(\lambda\) and \(Kappa\).
Through simulations across a wide range of conditions, we find that the
precision of effect sizes based on \(\lambda\) (\(Z_{\lambda}\)) are
less reliable than that those based on \(Kappa\) (\(Z_K\)), implying
that \(Z_K\) is a more robust effect size measure. Additionally, we
propose a two-sample test statistic that may be used to compare the
strength of phylogenetic signal among datasets, and provide an empirical
example to demonstrate its use. We conclude that estimates of
phylogenetic signal using Pagel's \(\lambda\) are often inaccurate, and
thus interpreting strength of phylogenetic signal in phenotypic datasets
based on this measure is compromised. By contrast, effect sizes obtained
from \(Kappa\) hold promise for characterizing phylogenetic signal, and
for comparing the strength of phylogenetic signal across datasets.

@@

All analyses were performed in R v3.6.0 (R Core Team 2019) using the
packages \texttt{geiger} (Harmon et al. 2008), \texttt{caper} (Orme et
al. 2013), \texttt{phytools} (Revell 2012), and \texttt{geomorph} (Adams
and Otárola-Castillo 2013; Adams et al. 2020). R-scripts are found in
the Supporting Information. \hfill\break

\emph{Results.} We found that the precision of \(\lambda_{est}\) varied
widely across simulation conditions. Predictably, precision improved as
the number of species increased (Figure 2). This confirmed earlier
findings of Boettiger et al.~(2012), and adhered to parametric
statistical theory. However, in many cases the set of \(\lambda_{est}\)
spanned nearly the entire range of possible values (e.g., \(n=32\);
\(\lambda_{in}=0.5\): \(\lambda_{est}= 0.0\to 0.985\)), revealing that
estimates of \(\lambda\) were not a reliable indicator of input
phylogenetic signal. Importantly, the precision of \(\lambda_{est}\) was
not uniform across all levels of phylogenetic signal, with the worst
precision at intermediate levels of signal (\(\lambda_{in}\approx0.5\)),
and improved precision as input levels approached the extremes of its
range (i.e., \(\lambda_{in}\rightarrow0\) \&
\(\lambda_{in}\rightarrow1\)). Thus, estimates of \(\lambda\) were least
reflective of the true input signal at intermediate values.
Additionally, even at large levels of species richness, we found that
the range of \(\lambda_{est}\) still encompassed a substantial portion
of possible values (e.g., \(n=512\); \(\lambda_{in}=0.5\):
\(\lambda_{est} = 0.32\to 0.68\)). Likewise, the same \(\lambda_{est}\)
could be obtained from datasets containing vastly different input levels
of phylogenetic signal (e.g., \(n=512\); \(\lambda_{est} = 0.5\);
\(\lambda_{in} = 0.25 \to 0.65\)). Note that these findings were
particularly unsettling when considered in light of our literature
survey. Over one quarter of the \(\lambda\) estimates obtained in
empirical studies (421 of 1,572) were between \(\lambda=0.25\) and
\(\lambda=0.75\) (Figure 1). Of those, 30\% were interpreted directly in
terms of the strength of phylogenetic signal that they represented
(e.g., small, intermediate, strong signal). \hfill\break

Finally, when \(\lambda\) was co-estimated with regression parameters in
PGLS regression, the results of our simulations were quite similar.
Here, regression parameters (\(\beta\)) were accurately estimated,
confirming earlier findings of Revell (2010) (see Supporting
Information). Additionally, estimates of phylogenetic signal were less
precise, and the spread of \(\lambda_{est}\) was similar to that
observed when \(\lambda\) was estimated for only the dependent variable
(Figure 3). Taken together, these findings reveal that \(\lambda_{est}\)
does not precisely characterize observed levels of phylogenetic signal
in phenotypic datasets, and that biological interpretations of the
strength of phylogenetic signal based on \(\lambda\) may be highly
inaccurate. \hfill\break

@@

The results above demonstate that \(\lambda\) is not a reliable estimate
of the phylogenetic signal in phenotypic data. As such, biological
interpretations of the strength of phylogenetic signal, and comparisons
of the magnitude of such effects across datasets, are severely
compromised when based on this parameter. As an alternative, we propose
that summary estimates of phylogenetic signal be converted to effect
sizes for interpretation and comparison. Statistically, a standardized
effect size may be found as:

@@

where \(\theta_{obs}\) is the observed test statistic, \(E(\theta)\) is
its expected value under the null hypothesis, and \(\sigma_\theta\) is
its standard error (Glass 1976; Cohen 1988; Rosenthal 1994).
\(Z_{\theta}\) expresses the magnitude of the effect in \(\theta_{obs}\)
by transforming the original test statistic to a standard normal deviate
(Glass 1976; Kelley and Preacher 2012). Typically, \(\theta_{obs}\) and
\(\sigma_\theta\) are estimated from the data, while \(E(\theta)\) is
obtained from the distribution of \(\theta\) derived from parametric
theory. However, recent advances in resampling theory (Collyer et al.
2015; Adams and Collyer 2016, 2019a) have shown that \(E(\theta)\) and
\(\sigma_\theta\) may also be obtained from an empirical sampling
distribution of \(\theta\) obtained from permutation procedures.
\hfill\break

Adams and Collyer (2019b) recently suggested that the strength of
phylogenetic signal could be represented as an effect size, based on the
\(Kappa\) statistic and its empirical sampling distribution from
permutation. Here we formalize that suggestion, resulting in an effect
size of:

@@

In this case, \(\lambda_{obs}\) and \(\hat\sigma_\lambda\) are
empirically derived using maximum likelihood. Note that under the null
hypothesis no phylogenetic signal is expected (Freckleton et al. 2002),
and thus \(E(\lambda)=0\) under this condition. \hfill\break

To evaluate the utility of \(Z_K\) and \(Z_\lambda\) we calculated both
effect sizes for the simulated datasets generated above, and summarized
the precision of each using its variance (\(\sigma^2_{Z_K}\) and
\(\sigma^2_{Z_\lambda}\)). Results are found in Figure 4. Here two
things are evident. First, estimates of \(Z_K\) track the input
phylogenetic signal in a more linear fashion than do estimates of
\(Z_\lambda\) (Figure 4A,B). Thus, actual changes in the strength of
phylogenetic signal are reflected more evenly in the corresponding
values of the effect size \(Z_K\). Second, the precision of \(Z_K\) is
considerably more stable as compared with \(Z_\lambda\). This may be
seen by calculating the coefficients of variation for the set of
precision estimates (i.e., \(\sigma^2_{Z_K}\) and
\(\sigma^2_{Z_\lambda}\)) across input levels of phylogenetic signal.
Here coefficients of variation in the precision of \(Z_K\) were an order
of magnitude smaller for than for \(Z_\lambda\) (Figure 4C,D). This
implied that estimates of the strength of phylogenetic signal were more
reliable and robust when using \(Z_K\) as compared with \(Z_\lambda\).
\hfill\break

@@

One important advantage of the approach advocated here is that the
resulting effect sizes (\(Z_K\)) are dimensionless, as the units of
measurement cancel out during their calculation {[}\textbf{S\&R??}{]}.
As a consequence, the effect sizes represent the strength of
phylogenetic signal on a common and comparable scale, measured in
standard deviation units, regardless of the initial units and scale of
the original phenotypic variables under investigation.

\hypertarget{section}{%
\subsubsection{}\label{section}}

Conceptually, this is akin to the conversion of data to their standard
normal deviates prior to their use in multivariate analysis, when the
original variables are expressed in different units or scales {[}see
{]}. \#\#\#

\hypertarget{section-1}{%
\paragraph{}\label{section-1}}

mathematical transformation or standardization of the trait dimensions,
so the variables are expressed in similar units n the variables in a
multivariate data set are on different scales,

Everitt, Brian; Hothorn, Torsten J (2011), An Introduction to Applied
Multivariate Analysis with R, Springer,

Also, Legendre\ldots{} Adams and Collyer. \#\#\#\#

Because of this standardization, the strength of phylogenetic signal
across datasets has meaning

something about comparisons having meaning\ldots{}

As such, characterizing the strength of phylogenetic signal with \(Z_K\)
facilitates a formal statistical comparison of values across continuous
traits of different units, scale, or even dimensionality (e.g.,
univariate traits using \(Kappa\), and multivariate traits using
\(K_{mult}\)).

@@

@@

@@

@@

@@

@@

>>>>

@@

@@

Evolutionary biologists commonly seek to describe the relative strength
of phylogenetic signal in phenotypic traits, to determine the extent to
which shared evolutionary history has influenced trait covariation among
taxa. This is often accomplished by interpreting empirical estimates of
\(\lambda\); with smaller values signifying `weak' phylogenetic signal,
while larger values are interpreted as `strong' phylogenetic signal
(e.g., De Meester et al. 2019; Pintanel et al. 2019; Su et al. 2019).
Other approaches for interpreting \(\lambda\) are more statistical. For
instance, some have evaluated whether the observed \(\lambda\) differs
from some expected value through the use of confidence intervals
(Vandelook et al. 2019) or by performing likelihood ratio tests that
compare the observed model fit to that obtained when \(\lambda=0\) or
\(\lambda=1\) (Freckleton et al. 2002; Cooper et al. 2010; Bose et al.
2019). Additionally, qualitative comparisons of \(\lambda\) estimates
obtained from multiple phenotypic traits have been used to infer whether
the strength of phylogenetic signal is greater in one trait as compared
to another (e.g., Liu et al. 2019; Bai et al. 2019). Indeed, statements
regarding the strength of phylogenetic signal based on \(\lambda\) are
rather common in the evolutionary literature. For instance, of the 204
papers published in 2019 that estimated and reported Pagel's \(\lambda\)
(found in Google.scholar), 40\% interpreted the strength of phylogenetic
signal for at least one phenotypic trait. Additionally, because nearly
half of the 1,572 \(\lambda\) values reported were near the limits of
the parameter (Figure 1), this percentage is even higher, as biological
interpretation of phylogenetic signal at the limits of \(\lambda\) are
known. \hfill\break

@@

In this study, we evaluate the precision of Pagel's \(\lambda\) for
estimating known levels of phylogenetic signal in phenotypic data. We
use computer simulations with differing numbers of species, differently
shaped phylogenies, and differing input levels of phylogenetic signal,
to explore the degree to which \(\lambda\) correctly identifies known
levels of phylogenetic signal, and under what circumstances. We find
that estimates of \(\lambda\) vary widely for a given input value of
phylogenetic signal, and that the precision in estimating \(\lambda\) is
not constant across its range. Rather, there is decreased precision when
input levels of phylogenetic signal are of intermediate strength.
Additionally, the same estimated values of \(\lambda\) may be obtained
from datasets containing vastly different input levels of phylogenetic
signal. Thus, \(\lambda\) is not a reliable estimate of the strength of
phylogenetic signal in phenotypic data. We then describe a standardized
effect size for measuring the strength of phylogenetic signal in
phenotypic datasets, and apply the concept to two common measures of
phylogenetic signal: \(\lambda\) and \(Kappa\). Through simulations
across a wide range of conditions, we find that the precision of effect
sizes based on \(\lambda\) (\(Z_{\lambda}\)) are less reliable than that
those based on \(Kappa\) (\(Z_K\)), implying that \(Z_K\) is a more
robust effect size measure. We also propose a two-sample test statistic
that may be used to compare the strength of phylogenetic signal among
datasets, and provide an empirical example to demonstrate its use. We
conclude that estimates of phylogenetic signal using Pagel's \(\lambda\)
are often inaccurate, and thus interpreting strength of phylogenetic
signal in phenotypic datasets based on this measure is compromised. By
contrast, effect sizes obtained from \(Kappa\) hold promise for
characterizing phylogenetic signal, and for comparing the strength of
phylogenetic signal across datasets.

@@

All analyses were performed in R v3.6.0 (R Core Team 2019) using the
packages \texttt{geiger} (Harmon et al. 2008), \texttt{caper} (Orme et
al. 2013), \texttt{phytools} (Revell 2012), and \texttt{geomorph} 3.2.1
(Adams and Otárola-Castillo 2013; Adams et al. 2020). R-scripts are
found in the Supporting Information. \hfill\break

\emph{Results.} We found that the precision of \(\lambda_{est}\) varied
widely across simulation conditions. Predictably, precision improved as
the number of species increased (Figure 2). This confirmed earlier
findings of Boettiger et al.~(2012), and adhered to parametric
statistical theory. However, in many cases the set of \(\lambda_{est}\)
spanned nearly the entire range of possible values (e.g., \(n=32\);
\(\lambda_{in}=0.5\): \(\lambda_{est}= 0.0\to 0.985\)), revealing that
estimates of \(\lambda\) were not a reliable indicator of input
phylogenetic signal. Importantly, the precision of \(\lambda_{est}\) was
not uniform across all levels of phylogenetic signal. The worst
precision was observed at intermediate levels of phylogenetic signal
(\(\lambda_{in}\approx0.5\)), while precision improved as input levels
approached the extremes of \(\lambda\)'s range (i.e.,
\(\lambda_{in}\rightarrow0\) \& \(\lambda_{in}\rightarrow1\)). Thus,
estimates of \(\lambda\) were least reflective of the true input signal
at intermediate values. Additionally, even at large levels of species
richness, we found that the range of \(\lambda_{est}\) still encompassed
a substantial portion of possible values (e.g., \(n=512\);
\(\lambda_{in}=0.5\): \(\lambda_{est} = 0.32\to 0.68\)). Likewise, the
same \(\lambda_{est}\) could be obtained from datasets containing vastly
different input levels of phylogenetic signal (e.g., \(n=512\);
\(\lambda_{est} = 0.5\); \(\lambda_{in} = 0.25 \to 0.65\)). These
findings were particularly unsettling when considered in light of our
literature survey. Over one quarter of the \(\lambda\) estimates
obtained in empirical studies (421 of 1,572) were between
\(\lambda=0.25\) and \(\lambda=0.75\) (Figure 1). This range reflected
the region that our simulations identified as being the least reliable
in terms of accurately characterizing levels of phylogenetic signal, yet
30\% of these empirical estimates were explicitly interpreted in terms
of the strength of phylogenetic signal that they represented (i.e.,
weak, intermediate, strong phylogenetic signal). \hfill\break

Finally, when \(\lambda\) was co-estimated with regression parameters in
PGLS regression, the results of our simulations were quite similar.
Here, regression parameters (\(\beta\)) were accurately estimated,
confirming earlier findings of Revell (2010) (see Supporting
Information). However, estimates of phylogenetic signal (\(\lambda\))
were less precise (Figure 3), and the spread of \(\lambda_{est}\) was
similar to that observed when \(\lambda\) was estimated for only the
dependent variable, as in Figure 2. Taken together, these findings
reveal that \(\lambda_{est}\) does not precisely characterize observed
levels of phylogenetic signal in phenotypic datasets, and that
biological interpretations of the strength of phylogenetic signal based
on \(\lambda\) may be highly inaccurate. \hfill\break

@@

The results above demonstate that \(\lambda\) is not a reliable estimate
of the phylogenetic signal in phenotypic data. As such, biological
interpretations of the strength of phylogenetic signal, and comparisons
of the magnitude of such effects across datasets are severely
compromised when based on this parameter. As an alternative, we propose
that summary estimates of phylogenetic signal be converted to effect
sizes for interpretation and comparison of the relative strength of
phylogenetic signal in phenotypic datasets. Statistically, a
standardized effect size may be found as:

@@

where \(\theta_{obs}\) is the observed test statistic, \(E(\theta)\) is
its expected value under the null hypothesis, and \(\sigma_\theta\) is
its standard error (Glass 1976; Cohen 1988; Rosenthal 1994).
\(Z_{\theta}\) expresses the magnitude of the effect in \(\theta_{obs}\)
by transforming the original test statistic to its standard normal
deviate (Glass 1976; Kelley and Preacher 2012). Typically,
\(\theta_{obs}\) and \(\sigma_\theta\) are estimated from the data,
while \(E(\theta)\) is obtained from the distribution of \(\theta\)
derived from parametric theory. However, recent advances in resampling
theory (Collyer et al. 2015; Adams and Collyer 2016, 2019a) have shown
that \(E(\theta)\) and \(\sigma_\theta\) may also be obtained from an
empirical sampling distribution of \(\theta\) obtained from permutation
procedures. \hfill\break

Adams and Collyer (2019b) suggested that the strength of phylogenetic
signal could be represented as an effect size, based on the \(Kappa\)
statistic and its empirical sampling distribution from permutation. Here
we formalize that suggestion, resulting in an effect size of:

@@

In this case, \(\lambda_{obs}\) and \(\hat\sigma_\lambda\) are
empirically derived using maximum likelihood. Note that under the null
hypothesis, no phylogenetic signal is expected (Freckleton et al. 2002),
and thus \(E(\lambda)=0\) under this condition. \hfill\break

To evaluate the utility of \(Z_K\) and \(Z_\lambda\) we calculated both
effect sizes for the simulated datasets generated above, and summarized
the precision of each using its variance (\(\sigma^2_{Z_K}\) and
\(\sigma^2_{Z_\lambda}\)). Results are found in Figure 4 (additional
results are found in the Supporting Information). Here two things are
evident. First, estimates of \(Z_K\) track the input phylogenetic signal
in a more linear fashion than do estimates of \(Z_\lambda\) (Figure
4A,B). Thus, actual changes in the strength of phylogenetic signal are
reflected more evenly in the corresponding values of the effect size
\(Z_K\). Second, the precision of \(Z_K\) is considerably more stable as
compared with \(Z_\lambda\). This may be seen by calculating the
coefficients of variation for the set of precision estimates (i.e.,
\(\sigma^2_{Z_K}\) and \(\sigma^2_{Z_\lambda}\)) across input levels of
phylogenetic signal. Here coefficients of variation in the precision of
\(Z_K\) were an order of magnitude smaller for than for \(Z_\lambda\)
(Figure 4C,D). This implied that estimates of the strength of
phylogenetic signal were more reliable and robust when using \(Z_K\) as
compared with \(Z_\lambda\). \hfill\break

@@

One important advantage of the approach advocated here is that the
resulting effect sizes (\(Z_K\)) are dimensionless, as the units of
measurement cancel out during the calculation of \(Z\) (Sokal and Rohlf
2012). As a consequence, the effect sizes represent the strength of
phylogenetic signal on a common and comparable scale, measured in
standard deviation units, regardless of the initial units and scale of
the original phenotypic variables under investigation. This means that
conceivably, the strength of phylogenetic signal may be compared across
datsets for phenotypic traits in different units and scale (e.g.,
behavioral and morphological traits), so long as they are continuous
variables. Note that this is directly related to the common practice of
converting data to their standard normal deviates prior to their use in
multivariate analysis, if the original variables are expressed in
different units or scales (see Everitt and Hothorn 2011; Legendre and
Legendre 2012; Adams and Collyer 2019b).

@@

To demonstrate the utility of \(\hat{Z}_{12}\) we performed an analysis
of the strength of phylogenetic signal in two phenotypic datasets from
species of plethodontid salamander. The data were part of a series of
studies examining macroevolutionary trends in phenotypic diversification
in this group (Baken and Adams 2019; Baken et al. 2020). Our dataset
contained surface area to volume ratios (SA:V) and relative body width
(\(\frac{BW}{SVL}\)) for 305 species (Figure 5A). For SA:V, 11 linear
body measurements from 2,781 individuals were taken, from which
estimates of the surface area and volume of the head, body, and tail
were calculated and subsequently combined to arrive at the SA:V for each
indiviual (for mathematical details see Baken et al. 2020). Species
means were then obtained. Likewise, body size (SVL) and body width (BW)
measurements were taken from 3,371 individuals, and species means of
relative body width (\(\frac{BW}{SVL}\)) were calculated (data from
Baken and Adams 2019). A time-dated molecular phylogeny for the group
(Bonett and Blair 2017) was then pruned to match the species in the
dataset, resulting in a phylogeny and corresponding phenotypic dataset
containing 305 species. The phylogenetic signal in each trait was then
characterized using \(Kappa\), which was converted to its effect size
(\(Z_K\)) using \texttt{geomorph} 3.2.1 (Adams and Otárola-Castillo
2013; Adams et al. 2020). Finally, the strength of phylogenetic signal
was compared across traits using \(\hat{Z}_{12}\) as described above
(\textbf{to be incorporated in \texttt{geomorph} upon manuscript
acceptance}). \hfill\break

\emph{Results.} Both SA:V and relative body width displayed significant
phylogenetic signal (\(Kappa_{SA:V}=0.7608\); \(P=0.001\);
\(Kappa_{BW/SVL}=0.2515\); \(P=0.001\)). For both phenotypic traits,
\(K_{obs}\) differed markedly from their corresponding permutation
distributions, which were found to overlap almost perfectly (Figure 5B).
However, while both traits displayed significant phylogenetic signal,
there was nearly a four-fold difference in the magnitude of their effect
sizes, with SA:V displaying the greater phylogenetic signal (Figure 5C).
Using the two-sample test statistic above, this difference was found to
be highly significant (\(\hat{Z}_{12}=4.13\); \(P=0.000036\)). Thus it
may be concluded that SA:V displays significantly stronger phylogenetic
signal than does relative body width, and that shared evolutionary
history has strongly influenced trait covariation among taxa for SA:V.
Biologically, this observation corresponds with the fact that tropical
species -- which form a monophyletic group within plethodontids --
display greater variation in SA:V which covaries with disparity in their
climatic niches (Baken et al. 2020). Thus, because of this
macroevolutionary association, strong phylogenetic signal in SA:V is to
be expected.

@@

\leavevmode\hypertarget{ref-Baken2019}{}%
Baken, E. K., and D. C. Adams. 2019. Macroevolution of arboreality in
salamanders. Ecology and Evolution 9:7005--7016.

\leavevmode\hypertarget{ref-Baken2020}{}%
Baken, E. K., L. E. Mellenthin, and D. C. Adams. 2020. Macroevolution of
desiccation‐related morphology in plethodontid salamanders as inferred
from a novel surface area to volume ratio estimation approach. Evolution
74:476--486.

@@

\leavevmode\hypertarget{ref-Bonett2017}{}%
Bonett, R. M., and A. L. Blair. 2017. Evidence for complex life cycle
constraints on salamander body form diversification. Proceedings of the
National Academy of Sciences, U.S.A. 114:9936--9941.

@@

\leavevmode\hypertarget{ref-Everitt2011}{}%
Everitt, B., and T. Hothorn. 2011. An introduction to applied
multivariate analysis with r. Springer Science \& Business Media.

@@

\leavevmode\hypertarget{ref-LegendreLegendre2012}{}%
Legendre, P., and L. Legendre. 2012. Numerical ecology. 3rd ed.
Elsevier, Amsterdam.

@@

\leavevmode\hypertarget{ref-SokalRohlf2012}{}%
Sokal, R. R., and F. J. Rohlf. 2012. Biometry. 4th ed. W.H. Freeman \&
Co., San Francisco.
